%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
% \usepackage{DejaVuSans}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Meni} \headerlastnamestyle{Sadigurschi} \\
	\vspace{2mm}
	{\faEnvelope\ \href{mailto:menisadi@gmail.com}{menisadi@gmail.com}} | {\faMobile\ 0546751163} | {\faMapMarker\ IL} | {\faLink\ \href{https://menisadi.github.io/}{menisadi.github.io}}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Summary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Summary}
\vspace{-5mm}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		$\bullet$  & {\skill{\quad Ph.D. in Computer Science with a thesis on machine learning and data privacy.}} \\
		$\bullet$  & {\skill{\quad Experienced in the use of contemporary platforms related to the fields of data science and machine learning.}} \\
  		$\bullet$  & {\skill{\quad Main author publications in top-tier conferences.}} \\
            $\bullet$  & {\skill{\quad Currently working as a Data Scientist at Intent IQ, applying machine learning and algorithms research in production.}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-10mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Intent IQ}
	{Data Scientist}
	{Feb 2023 – Present}
	{}
    {Applying machine learning and algorithms research in a production environment. Israel – Hybrid.}
	\cventry
	{Ben-Gurion University of the Negev}
	{Teaching Assistant}
	{2015 – 2022}
	{}
    {Teaching: Discrete Structures and Combinatorics, Design of Algorithms, Graphs, \hspace{20em} Introduction to machine learning, Adaptive data analysis.}	
	\cventry
	{Georgetown University (remote)}
	{Research Assistant}
	{2016 – 2018}
	{}
    {Working with Prof. Kobi Nissim from Harvard University and Georgetown University. \hspace{20em}
    Working on optimization and Implementations of private learning algorithms.}
	% \cventry
	% {\textit{Israel Defense Forces}}
	% {Analyst}
	% {2009 – 2011}
	% {}
 %    {Research and analysis of intelligence data, providing decision-makers with complete\hspace{20em}
 %    and comprehensive information.}
\end{cventries}
\vspace{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Ben-Gurion University of the Negev}
	{Ph.D in Computer Science}
	{2018 – 2022}
	{}
	{Title: A Study of Privacy and Compression in Learning Theory}
	\cventry
	{Ben-Gurion University of the Negev}
	{M.Sc in Computer Science}	
    {2016 – 2018}
	{\textbf{GPA: 98}}	    
	{Title: Compression-Schemes for Real-Valued Learners}	
	\cventry
	{Ben-Gurion University of the Negev}	
	{B.Sc in Mathematics and Computer Science}
	{2013 – 2016}
	{\textbf{GPA: 93}}
    {}
\end{cventries}

\vspace{-5mm}

\cvsection{Publications}
\begin{cventries}
	\cventry
	{Establishing agnostic sample compression schemes for regression with near-optimal rates. \textbf{Published at ICML 24 (Spotlight)}}
	{Agnostic Sample Compression Schemes for Regression}
	{}
	{}
	{}

	\vspace{-5mm}
	\cventry
	{Introducing relaxed adversarial streaming models that allow practical algorithm design with provable guarantees. \textbf{Published at ESA 23}}
	{Relaxed Models for Adversarial Streaming: The Advice Model and the Bounded Interruptions Model}
	{}
	{}
	{}

	\vspace{-5mm}
	\cventry
	{A fundamental study regarding the possible extensions of adaptive data analysis tools such that they could be used with correlated observations. \textbf{Published at ICML 22}}
	{Adaptive Data Analysis with Correlated Observations}
	{}
	{%\href{https://arxiv.org/abs/2201.08704}{https://arxiv.org/abs/2201.08704}
    }
	{}
	
	\vspace{-5mm}
	\cventry
	{A privacy preserving learning algorithm for the Axis-Aligned Rectangles problem which has near-optimal sample complexity. \textbf{Published at NeurIPS 21}}
	{On the Sample Complexity of Privately Learning Axis-Aligned Rectangles}
	{}
	{%\href{https://arxiv.org/abs/2107.11526}{https://arxiv.org/abs/2107.11526}
    }
	{}
	
	\vspace{-5mm}
	\cventry
	{An algorithmically efficient version of the learner-to-compression scheme conversion which is also extended to regression hypotheses classes. \textbf{Published at ALT 19}}
	{Sample Compression for Real-Valued Learners}
	{}
	{%\href{https://arxiv.org/abs/1805.08254}{https://arxiv.org/abs/1805.08254}
    }
	{}
\end{cventries}
\vspace{-6mm}	
\cvsection{Awards}
\begin{cvhonors}
	\cvhonor
	{Excellence in teaching award}
	{\scriptsize{Ben-Gurion University of the Negev}}
	{}
	{2022}
	\cvhonor
	{Scholarship for High-tech excellent doctoral students}
	{\scriptsize{The Kreitman school of Advanced Graduate Studies}}
	{}
	{2019}
	\cvhonor
	{Dean’s list}
	{\scriptsize{Ben-Gurion University of the Negev}}
	{}
	{2018}	
	\cvhonor
	{Suzan Zlotowski Prize for Academic Excellence}
	{\scriptsize{Ben-Gurion University of the Negev}}
	{}
	{2014}	
	\cvhonor
	{Schulich Leader Scholarships Winner}
	{\scriptsize{The Schulich Foundation}}
	{}
	{2013}	
\end{cvhonors}
\cvsection{Skills}
\vspace{-5mm}
\begin{cventries}
	\cventry
	{\tiny}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming:  & {\skill{\quad Experienced with Python and various libraries such as Pandas, Scikit-learn and TensorFlow}} \\
  Research:  & {\skill{\quad Has the ability to delve deeper, learn complex and new concepts in order to attack challenging problems.}} \\
		Languages:  & {\skill{ \quad Hebrew, English, Portuguese}} \\
		\end{tabular}}}
	{\tiny}
	{\tiny}
	{\tiny}
\end{cventries}
\end{document}